\section{Motivation}
The current flood of capital to invest in Web3 projects demonstrates the desire for entry into this booming industry. In contrast, there is a lack of experience and programmers who can make this change possible. For this reason, one can observe a convoluted development and investment in any project that could promise future value. Qualitative development is expensive due to low availability - we need more efficient and durable web3 projects. \\
With LionConnect event we want to use this market situation to benefit both, developers and investors. This platform organizes the needs of highest-seeking investors and web3 developers by matching value and investment. It allows investors to find value in the most academically advanced projects which have proven themselves through rigorous application and competition. On the other hand, developers can use this incentivizing space to find fair funding for their passion and find accelerated access to the emerging web3 space. \\
The event will host the best projects created by experienced developers and academic blockchain clubs which had to pass an application process. During the event, we intend to identify the highest quality applications with highest value for investors by letting the distinguished teams prove their project quality through rigorous peer-review challenges. These challenges will be incentivized by giving rewards and increasing ones own project rating by finding vulnerabilities in others. Such a competitive approach has already proven itself in, e.g., cryptography development\footnote{https://csrc.nist.gov/projects/cryptographic-standards-and-guidelines/archived-crypto-projects/aes-development}.\\
To bring smart money and the highest industry standard together our event will have an application process for investors and developers. Our network to blockchain clubs and universities around the globe, involvement in conferences, and (past) partnerships to investors allow us to invite the most advanced and innovative projects together with the best and most supportive funding. 
\\\\
As unique interface between academia, developers, industry, and investors, there is a potential to bring together resources in a well-organised way. During LionHack our Blockchain Club has demonstrated great passion and motivation in successfully organizing such events. With our greatest effort to use our network, attention to detail, and passion to plan and create LionConnect, we will be able to provide the platform to structurally satisfy the needs of all participating parties. A web3 incentive system will ensure the quality and forward movement of this project.
After LionHack it was clear that there is a need for such events to improve the structure and catalyze the web3 development process. Be part of the movement and plan your strategy efficiently and ahead of time: No matter whether you're developer, entrepreneur, investor, or student.

Showcase how web3 can support such events and make them more efficient.